Improving \textsl{Gaia} parallaxes with a data-driven model of the color--magnitude diagram

### 2017-03-14 paperDistance/paper.tex
posterior outputs warnings

@@

Note the dangers of using the stars from our output in hierarchical inferences!

>>>>

DWH: Placeholder for the output format for our data products. Should
be the last paragraph or two of this section.

@@

The outputs of this project include posterior pdfs and posterior
samplings for stellar parallaxes or distances.
It is tempting to treat these outputs as equivalent to some kind of catalog of
measurements, as we treated the original parallax measurements from \tgas.
That is, it is tempting to treat these as simply ``better'' measurements.
Taken one star at a time, this is permitted and true, and the basis for our
claim that we have de-noised the \tgas\ Catalog.
However, there are important differences, as there are with all
probabilistic catalogs (HOGG CITE LANG, FINKBEINER), between the
measurements and the de-noised measurements.
The most important difference, for users of our output, between our
output and the \tgas\ data input, is that the \tgas\ data is the representation
of a likelihood function, whereas our ouptut is a
representation of a posterior pdf, one per star.
If used naively, posterior information can lead to serious statistical
errors, because each data point has had a prior multiplied in.
Effectively multiplicative uses of the data will effectively take the prior
pdf to a large power.
We have given examples of correct uses of posterior samplings or pdfs
for subsequent inferences in previous work (HOGG CITE ECC and DFM); we
encourage power-users to consult those methodological
contributions before engaging with these outputs.
